Monte Carlo and bootstrap for ALL parameters with tables

### 2024-09-07 Last_tables/All3_tab_algo6.Rmd
It seems to work

```{r}
# Function to sample at random following the grid
# Algorithm 6 in the report (2024/10/02 version)
sampling_grid1 <- function(i, c_dim){
  cells_x <- c()
  cells_y <- c()
  raw <- c()
  elt <- i
  while (elt < (1000*1000)) {
    raw <- append(raw, elt)
    elt <- elt+10
  }
  for (j in raw) {
    cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, j%%23))
    cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, (j-(j%%23))/23) )
  }
  return(data.frame(x = cells_x, y = cells_y))
}
```

```{r}
# Function to sample at random following the grid
# Algorithm 7 in the report (2024/10/02 version)
sampling_grid2 <- function(i,c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

>>>>

```{r}
# Function to sample at random following the grid
# Algorithm 6 in the report (2024/10/02 version)
sampling_grid1 <- function(i, c_dim){
  # i = 1,...,10
  cells_x <- c()
  cells_y <- c()
  raw <- c()
  elt <- (i-1)*10
  while (elt < (100*1000)) {
    raw <- append(raw, elt)
    elt <- elt+100
  }
  for (j in raw) {
    cells_x <- append(cells_x, ifelse(j%%1000 == 0, 1000, j%%1000))
    cells_y <- append(cells_y, ifelse(j%%1000 == 0, ((j-(j%%1000))/1000) - 1, (j-(j%%1000))/1000) )
  }
  cells_y <- cells_y*10
  a <- mapply(function(x){runif(1, x, x+10)}, cells_x)
  b <- mapply(function(x){runif(1, x, x+10)}, cells_y)
  return(data.frame(x = a, y = b))
}
```

```{r}
# Function to sample at random following the grid
# Algorithm 7 in the report (2024/10/02 version)
sampling_grid2 <- function(i,c_dim){
  # i = 1,...,10
  i <- i-1
random_points <- data.frame(x = numeric(), y = numeric())

### 2024-09-07 Last_tables/All3_tab_algo7.Rmd
It seems to work

```{r}
# Monte carlo alone
# Number of MC iterations
B0 <- 10000 # 10 # 
```

```{r}
# Monte Carlo and bootstrap
# Number of MC iterations
B1 <- 1000 # 5 # 
# Number of bootstrap replications
B2 <- 400 # 5 # 
```

>>>>

```{r}
# Monte carlo alone
# Number of MC iterations
B0 <- 10 # 10000 # 
```

```{r}
# Monte Carlo and bootstrap
# Number of MC iterations
B1 <- 5 # 1000 # 
# Number of bootstrap replications
B2 <- 5 # 400 # 
```
